Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-10-13 manuscript/paper-tycho.tex
Dwnstream spectra w/lines fit/excised
Update spectrum fitting code to handle both Si and S lines
Added new table with fit data (line energies/eqwidths) for manuscript
Damping fit, mE LaTeX tables; SN1006 model tables
Nice tables for damping model fit outputs.
Generate FWHM tables for SN 1006 parameters

%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
%\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}

@@

@@

\section{Derivation for synchrotron roll-off and diffusion}

@@

Assume that a DSA model explains the observed e-/synchrotron spectra
cut-off/roll-off.  We estimate e- cut-off energy by equating
$\tau_{\mt{accel}} = \tau_{\mt{synch}}$.  This gives (Parizot et al., 2006):
\[
    \frac{3r}{r-1} \frac{r D_d + D_u}{v_s^2} = \frac{1}{b B^2 \Ecut}
\]
(\emph{I don't know if this equality was designed to exactly obtain the electron
cutoff energy, or is just a rough/scaling relation -- pull up Drury (1983) to
check this})
Following through the arguments/assumptions in Parizot et al. (2006) yields
(using $13.3 \unit{erg} = 8.3 \unit{TeV}$):
\[
    \Ecut =
        \left( 13.3 \unit{erg} \right)^{\frac{2}{1+\mu}}
        \left( \frac{B_0}{100 \muG} \right)^{-\frac{1}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm\;s^{-1}}} \right)^{\frac{2}{1+\mu}}
        \eta^{-\frac{1}{1+\mu}}
\]
Now, we can convert this cut-off e- energy to a roll-off synchrotron energy by
invoking the delta function assumption $\nu_{\mt{cut}} = c_m \Ecut^2 B$ with
$c_m = 1.822 \times 10^{18}$.
(\emph{Again, I don't know if this is an equality or just a scaling.  We'd need
to relate the electron spectrum cut-off to the derived synchrotron spectrum
cut-off, as is done (I think) by Zirakashvili and Aharonian (2007).})
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \eta^{-\frac{2}{1+\mu}}
\]
In the case of $\mu = 1$ this yields:
\[
    \nu_{\mt{cut}} = (0.133 \unit{keV} / h)
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{2}
        \eta^{-1}
\]
For $\mu \neq 1$ this is no longer independent of magnetic field.  But,
there is hope.  Rewrite this in terms of $\eta_2$ using
$\eta = \eta_2 E_2^{1-\mu}$ and write:
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( E_2 \right)^{-\frac{2(1-\mu)}{1+\mu}}
        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
\]
With $E_2 = \left( (2 \unit{keV}/h) / (c_m B) \right)^{1/2}$, or
$E_2 = \left( 0.2657 \unit{erg^2\;G} / B \right)^{1/2}$, we obtain:
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( \frac{0.2657 \unit{erg^2\;G}}{B} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
\]
And, the magnetic field terms cancel!  Hey presto.
Our final usable result is:
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( 0.2657 \unit{erg^2\;G} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
\]

>>>>

%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
%\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
%\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
\documentclass[iop, apj, numberedappendix]{emulateapj}

@@

\begin{table*}
    \footnotesize
    \centering
    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
    \input{tab-spec-pt2.tex}
\end{table*}

% TODO add text explaining this table (!!!!!!!!!!!!!)

@@

\section{Best fit width-energy curve $m_\mt{E}$ values}

\begin{table*}[ht]
    \footnotesize
    \centering
    \caption{$m_\mt{E}$ computed from best loss-limited fit FWHMs}
    \input{tab-fits-mE.tex}
\end{table*}

\clearpage
\section{Magnetic damping best fit tables}

\begin{table*}[ht]
    \scriptsize
    \centering
    \caption{Damped fits to individual regions, Filament 1, $\mu = 1$}
    \input{tab-fits-damp-f1.tex}
\end{table*}

\begin{table*}[ht]
    \scriptsize
    \centering
    \caption{Damped fits to individual regions, Filament 2, $\mu = 1$}
    \input{tab-fits-damp-f2.tex}
\end{table*}

\begin{table*}[ht]
    \scriptsize
    \centering
    \caption{Damped fits to individual regions, Filament 2 (cont.), $\mu = 1$}
    \input{tab-fits-damp-f2-pt2.tex}
\end{table*}

\begin{table*}[ht]
    \scriptsize
    \centering
    \caption{Damped fits to individual regions, Filament 3, $\mu = 1$}
    \input{tab-fits-damp-f3.tex}
\end{table*}

\begin{table*}[ht]
    \scriptsize
    \centering
    \caption{Damped fits to individual regions, Filament 4, $\mu = 1$}
    \input{tab-fits-damp-f4.tex}
\end{table*}

\begin{table*}[ht]
    \scriptsize
    \centering
    \caption{Damped fits to individual regions, Filament 5, $\mu = 1$}
    \input{tab-fits-damp-f5.tex}
\end{table*}

\clearpage
\section{Derivation for synchrotron roll-off and diffusion}

@@

Assume that a DSA model explains the observed e-/synchrotron spectra
cut-off/roll-off.  We estimate e- cut-off energy by equating
$\tau_{\mt{accel}} = \tau_{\mt{synch}}$.  This gives (Parizot et al., 2006):
\begin{equation}
    \frac{3r}{r-1} \frac{r D_d + D_u}{v_s^2} = \frac{1}{b B^2 \Ecut}
\end{equation}
(\emph{I don't know if this equality was designed to exactly obtain the electron
cutoff energy, or is just a rough/scaling relation -- pull up Drury (1983) to
check this})
Following through the arguments/assumptions in Parizot et al. (2006) yields
(using $13.3 \unit{erg} = 8.3 \unit{TeV}$):
\begin{equation}
    \Ecut =
        \left( 13.3 \unit{erg} \right)^{\frac{2}{1+\mu}}
        \left( \frac{B_0}{100 \muG} \right)^{-\frac{1}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm\;s^{-1}}} \right)^{\frac{2}{1+\mu}}
        \eta^{-\frac{1}{1+\mu}}
\end{equation}
Now, we can convert this cut-off e- energy to a roll-off synchrotron energy by
invoking the delta function assumption $\nu_{\mt{cut}} = c_m \Ecut^2 B$ with
$c_m = 1.822 \times 10^{18}$.
(\emph{Again, I don't know if this is an equality or just a scaling.  We'd need
to relate the electron spectrum cut-off to the derived synchrotron spectrum
cut-off, as is done (I think) by Zirakashvili and Aharonian (2007).})
\begin{equation}
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \eta^{-\frac{2}{1+\mu}}
\end{equation}
In the case of $\mu = 1$ this yields:
\begin{equation}
    \nu_{\mt{cut}} = (0.133 \unit{keV} / h)
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{2}
        \eta^{-1}
\end{equation}
For $\mu \neq 1$ this is no longer independent of magnetic field.  But,
there is hope.  Rewrite this in terms of $\eta_2$ using
$\eta = \eta_2 E_2^{1-\mu}$ and write:
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( E_2 \right)^{-\frac{2(1-\mu)}{1+\mu}}
        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
\]
With $E_2 = \left( (2 \unit{keV}/h) / (c_m B) \right)^{1/2}$, or
$E_2 = \left( 0.2657 \unit{erg^2\;G} / B \right)^{1/2}$, we obtain:
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( \frac{0.2657 \unit{erg^2\;G}}{B} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
\]
And, the magnetic field terms cancel!  Hey presto.
Our final usable result is:
\begin{equation}
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( 0.2657 \unit{erg^2\;G} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
\end{equation}
